Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-05-01 analysis/paper/supplement.Rmd
add profiling to Supp

>>>>

# Profiling

Profiling with the `Rprof` function can reveal which parts of a function take the longest. On a test run with 1 million cells in the weight raster and 10 landings we profiled the performance of the ILCP and MST methods. Constructing the graph took ~ 4 s for both methods. For the ILCP method, the iteratively determining the shortest path is the only other step that takes more that a second to run. Each iteration is relatively fast but must be repeated for each landing. For the MST method, the longest running step is the building of the second graph which is used to determine the MST. Determining the shortest path to connect the parts of the MST also takes about 2 seconds.

```{r profiling-ilcp, fig.cap="Profiling results for the ILCP method showing functions that take > 1 s to run on a cost raster with 1 million cells and 10 landings. Functions higher in the call stack are called by functions lower down.", fig.height=2}
if(!file.exists(here::here("analysis/data/derived_data/ilcp_Rprof.out"))){
  source(here::here("analysis/scripts/test_profile.R"), keep.source = TRUE)
}

profstat(here::here("analysis/data/derived_data/ilcp_Rprof.out"))

# interactive version
# profvis::profvis(prof_input = here::here("analysis/data/derived_data/ilcp_Rprof.out"))
```

```{r profiling-mst, fig.cap="Profiling results for the MST method showing functions that take > 1 s to run on a cost raster with 1 million cells. Functions higher in the call stack are called by functions lower down.", fig.height=5}
profstat(here::here("analysis/data/derived_data/mst_Rprof.out"))
```
